\section{Introduction}

% This is an introduction~\cite{Domingos:2015}
% \noindent
% \textbf{RQ1:} How is \ML used inside \RE tools?
% 
% \noindent
% \textbf{RQ2:} Is using \ML inside \RE tools beneficial?
% 
% \noindent
% \textbf{RQ3}: What \ML task(s) is (are) used for which purpose in \RE?
% 
% \noindent
% \textbf{RQ4}: Which model types are used to perform the \RE tasks?
% 
% \noindent
% \textbf{RQ5}: How are \ML features extracted/selected to guide \RE tasks?
% \parisa{just kept the old RQ for comparision}
Machine learning algorithms have been shown to have considerable practical
importance in many application domains. This is especially true of domains where
large databases are available and a need for exploring some kind of consistency
exists or, domains where a program needs to adapt itself to
changes~\cite{Zhang2002}. Requirements engineering is a critical part of
software engineering and it seems appropriate to use machine learning methods
for requirements engineering tasks. Because requirements specification documents
are mainly given in natural language, \ML can be useful by emulating human
processing.
\\
This paper aims to present a survey of how ML benefits existing RE
approaches. More precisely, we pursue the following research questions: \\
\noindent
\textbf{RQ1:} What is the current state of the practice in \ML${\&}$\RE?

\noindent
\textbf{RQ2:} What types of learning methods are used when \ML is applied to
\RE?

\noindent
\textbf{RQ3:} Which are the \RE problems that currently use \ML methods?

\noindent
\textbf{RQ4:} Is using \ML methods improving \RE?

To reply to these research questions we have performed a literature review,
split into data preparation, data collection, and data analysis phase. First, a search string
was prepared based on the research questions, then a search was performed over a
predefined set of databases and all identified studies were assessed by means of
title and abstract. Our literature review is not meant to be an exhaustive study
of the field -- rather we are offering a snapshot of the current
state-of-the-art by borrowing some techniques from Systematic Literature
Reviewing.\\
The major contributions of this article are as follows:

\begin{itemize}
    \item We provide an overview of the current state of the art of some of the
    challenges \RE faces that may be handled through \ML techniques. We focus on
    two important aspects:
    \begin{itemize}
        \item Providing an overview of the \ML problem categories
        (classification, regression, clustering, etc.) in use for the support of
        \RE tasks (elicitation, analysis, validation and management).
        \item Providing an overview of the common \ML models (decision tree,
        K-Nearest Neighbors, Naive Bayesian, etc.) for tackling \RE problems and
        the data sets if available.
    \end{itemize}
    \item We analyze the literature to discover trends and lessons on the use of \ML in \RE.
\end{itemize}
The paper is organized as follows. The rest of this section provides
background information on \ML and \RE required to understand the remaining of
the paper. Section~\ref{sec:contributions} provides an overview of \RE tasks
where \ML has been used. In section~\ref{sec:discussion} we summarize the major
findings of our study. Finally, in section~\ref{sec:threats_to_validity} we
state the threats to the validity of our work and section~\ref{sec:conclusion}
concludes the paper.
\input{text/machine_learning}
\input{text/req_engineering}
\input{text/preprocessing}