\subsection{Requirements Engineering}

Software systems are developed over millions of lines of code, number of modules
and documents. The primary goal of the software system is to satisfy users by
developing the software that can meet their needs and expectations. This goal is
achievable by applying different methodologies and engineering techniques. One
of the key factor is to understand and identify the needs of users, also known
as, software requirements. Software requirement engineering is the process that
helps to determine the requirements in a systematic way to know what
functionalities the targeted system should have to fulfil user's needs. Formally
RE is defined as \cite{Zave:1997:CRE:267580.267581}:\\
\begin{quote}
``Requirements engineering is the branch of software engineering concerned with the real-world
goals for, functions of, and constraints on software systems. It is also concerned with the
relationship of these factors to precise specifications of software behavior, and to their evolution
over time and across software families."
\end{quote}
Software requirements plays a key role in the success of a project. In the USA, a
survey was conducted over 8380 projects by 350 companies to know the project
failure rates. The report \cite{StandishReport} results showed only 16.2\% projects were
completed successfully and one-half (52.7\%) of projects met with challenges and
were completed with partial functionalities, time delays and over budget. Almost
31\% of the projects were never completed. The main cause told by the executive
managers was poor requirements engineering. The main culprits were the lack of
user involvement (13\%), requirements incompleteness (12\%), changing requirements
(11\%), unrealistic expectations (6\%), and unclear objectives
(5\%). \\
Software requirement engineering has mainly four phases; \emph{requirement
elicitation}, \emph{requirement analysis}, \emph{requirement documentation} and
\emph{requirement verification} \cite {Kotonya:1998}. Requirement elicitation
\cite{Coughlan:2002, Zowghi2005} helps to understand the
stakeholders needs, e.g. what features he wants in the software.
Requirement elicitation techniques are mostly derived by the social sciences,
organizational theory, knowledge engineering and practical experience. For
requirements elicitation, different techniques exist in the literature that
include interviews, questionaires and ethnography\levi{Why?} etc.
Requirement analysis \cite{Nuseibeh:2000} is the next step
after requirement elicitation. In this phase, software requirements are analyzed
to check for conflicts and consistency of requirements. It is also makes sure
that the requirements are clear, complete and consistent\levi{2X consistent}.
Furthermore, the agreed requirements are documented. This documentation has a clear and precise
definition of the system functionalities. It also acts as an agreement between
stakeholders and developers. These functionalities and requirements\levi{either
use one or the other} are documented usually as diagrams, mathematically
formulae or natural languages.

These documents are used and iterated upon until the end of the projects.
System requirements are classified into business requirements, user requirments,
functional requirements (FR) and non-functional requirements (NFR). Functional
requirements are the system requirements that include the main features and
characteristics of the desired system. Non-functional requirements are the
system properties and constraints \cite{Davis:1993, Glinz}. NFRs set the
criteria for judging the operation of the system e.g.
performance, availability or reliability. Business requirements are specified to
address business objectives, vision, and goals. It is defined at a high level to
keep the knowledge from organization or company side for designing the products.
User requirements are the wish list for the system from users\levi{I don't
think the intersection between FRs, NFRs, BRs and URs is empty}.
User requirements are valuable for ensuring the system performs similarly as users wanted it to do.
